% !TeX root = book.tex
\chapter{Spaces and Forms}
It is hardly necessary to explain what is different between a wild forest and well maintained parks or orderly forests planted by men. With all the differences, however, they have so much in common that to an alien who does not know the taste of mushrooms and cannot appreciate the charm of manicured lawns, woods will appear to be a continuous green area inhabited by objects of different heights and shapes, which we call trees. Similar things happen when you compare the contents of this chapter with Chapter 2 of [VA I], dedicated to the coordinate vector space. Abstract linear spaces, whose elements are called vectors and for which reason we often call it the vector space, are introduced axiomatically. The corresponding axiom system is essentially further developed by G. Peano (1888), well adapted to the theory of linear mappings (particularly, linear operators), which occupies a central place in linear algebra. The concept of a matrix at the same time seems to fade into the background. Of paramount importance are the invariant properties of the objects under study, ones that are independent of the choice of basis. 

However, before delving into the abstract forest, it is recommended that we once again walk through the well-kept parks - a specific space of row vectors of length $n$. We intentionally went for a partial repetition of the known material to smooth the roughness of the abstract.
\input{chap01/1}
\input{chap01/2}
\input{chap01/3}
\input{chap01/4}